\documentclass[12pt]{article}
\usepackage{custom}

% Data reading
\newcommand{\data}[1]{\input{../output/constants/#1.txt}\unskip}

% External references for any separately compiled online appendix.
\usepackage{xr}
\externaldocument{"si"}

\begin{document}
\title{Broad Validity of the First-Order Approach in Moral Hazard%
\thanks{We are especially grateful to Lucas Maestri for originating key ideas in this paper. We also thank Humberto Moreira and Juuso Toikka for their valuable comments.}
}

\author{Eduardo M. Azevedo% 
\thanks{Wharton: 3733 Spruce Street, Philadelphia, PA 19104: eazevedo@wharton.upenn.edu, \url{https://eduardomazevedo.github.io/.}}
\and Ilan Wolff% 
\thanks{Wharton: 3733 Spruce Street, Philadelphia, PA 19104. ijwolff@wharton.upenn.edu.}
}

\date{
First version: March 7, 2025 \\
This version: \today}

\maketitle

\begin{abstract}%
The first-order approach (FOA) is the main tool in the study of the pure moral hazard principal-agent problem. Although many existing results rely on the FOA, its validity has been established only under relatively restrictive assumptions. We contribute three main findings.

First, we demonstrate in a broad array of examples that the FOA frequently fails when the agent's reservation utility is low (such as in principal-optimal contracts). However, the FOA holds when the agent's reservation utility is at least moderately high (such as in competitive settings where agents receive high rents).

Second, our main theorem shows that the FOA is valid in a standard limited liability model when the agent's reservation utility is sufficiently high. The theorem also establishes existence and uniqueness of the optimal contract.

Third, we use the FOA to derive tractable optimal contracts across a broad array of settings. These contracts are both simple and intuitive. Under log utility, option contracts are optimal for numerous common output distributions (including Gaussian, exponential, binomial, Gamma, and Laplace).%
\end{abstract}

\newpage

\section{Introduction}
\label{sec:introduction}
\input{introduction}

\section{Examples and Literature Review}
\label{sec:examples}
\input{examples}

\section{Model}
\label{sec:model}
\input{model}

\section{Main Result}
\label{sec:main-result}
\input{main-result}

\section{Proof of the Main Result}
\label{sec:main-result-proof}
\input{proof-main-result}

\section{Applications and Extensions}
\label{sec:applications}
\input{calculus}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\bibliographystyle{aer}
\bibliography{bibliography}

\appendix
\newpage
\begin{center}
{\huge Appendix}{\huge\par}
\par\end{center}

\section{Proofs\label{sec:appendix-proofs}}
\input{appendix-proofs}

\end{document}
